%!TEX root = paper.tex
I present the estimation results under the other two settings of
participation constraints (action space) here.
The specification of choice set $\mathbf{C}_i$ here is the same as which in the main text, i.e.,
$3 \leq |\mathbf{C}_i| \leq 5$.

First, I try to shrink the action space and set
$p^{i}_{min} = \max\{0, ~p^{i}_{obs}-1000\}, ~ p^{i}_{max} = p^{i}_{obs} + 1000$.
The estimation results are shown in \Cref{table: estimates (min_size=3 max_size=5 margin=1000)}.
\input{\tables/estimates_min_size_3_max_size_5_margin_1000.tex}
As \Cref{table: estimates (min_size=3 max_size=5 margin=1000)} shows, the estimates of $\beta$
are slightly higher than $\hat{\beta} = \estbeta$ in the main text. But the standard error of $\hat{\beta}$ for
$\alpha = 0.33$ is extremely large, which implies there might be a weak identification problem
when the action space is small. Thus, the specification of action space is less appropriate than
which in the main text.

Second, I try to expand the action space and set
$p^{i}_{min} = \max\{0, ~p^{i}_{obs}-3000\}, ~ p^{i}_{max} = p^{i}_{obs} + 3000$.
The estimation results are shown in \Cref{table: estimates (min_size=3 max_size=5 margin=3000)}
below.

\input{\tables/estimates_min_size_3_max_size_5_margin_3000.tex}

As \Cref{table: estimates (min_size=3 max_size=5 margin=3000)} shows, the estimates of
$\beta$ are higher than $\hat{\beta} = \estbeta$ in the main text. But $\hat{\beta} = 0.61$ for $\alpha=0.5$ is still not far away
from $\hat{\beta} = \estbeta$.

Notice that in both
\Cref{table: estimates (min_size=3 max_size=5 margin=1000)}
and
\Cref{table: estimates (min_size=3 max_size=5 margin=3000)},
the estimates of $\beta$ with small standard errors vary from 0.48 to 0.61, thus, $\hat{\beta} = 0.45$ is a conservative estimate.
To conclude, the specification of action space in the main text is appropriate for
my analysis.